Inpainting with controlled frequency suppression in the Fourier domain

### 2011-06-23 project/Paper/paper.tex
! Finished paper review

%\usepackage{times}
%\usepackage{balance}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage[pdftex]{hyperref}
\usepackage[utf8]{inputenc}

@@

\subsubsection{Gradient descent}
\label{gradient_descent}
We optimize all parameters at once using a method called gradient descent. Since our cost function is based on measurements, we cannot derive it with respect to individual parameters and have to determine the gradient with finite differences. Besides weighting the parameters with respect to their improvements (which gives us the slope), we also defined a momentum term that should help us to overcome local minima (see figure \ref{gradient_descent_figure}).

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/framing_artifacts.png}
\caption{Due to the momentum, the cost function does not strictly decrease.}
\label{gradient_descent_figure}
\end{figure}

@@

\begin{table*}
\centering
\begin{tabular}{|l|p{6cm}|p{6cm}|}
\hline
Function & Advantages & Disadvantages \\
\hline
$E + T$ & Easy to understand and everywhere a good gradient & Linear improvement does not necessarily follow one's intuition about the ordering of results \\
\hline
$\exp(E)+\exp(T)$ & Fast increase for both error and time & Not enough gradient for very low $E$ and $T$ values \\
\hline
$(1-\exp(E))*(1-\exp(T))$ & Allows very large times for very low errors & Also true vice versa, i.e. a minimization in time \\
\hline
$\begin{cases}
E & \text{if }T<60\\
E+\exp(T/60 - 1) - 1 & \text{otherwise}
\end{cases}$ & Continuous function that optimizes for error only when the time is below a certain value but penalizes long times. & Seems to work quite well and therefore used by us \\
\hline
\end{tabular}
\caption{Various cost functions used in the optimization process.}
\label{cost_functions}
\end{table*}

\subsubsection{Sample data}
We used the three images provided for the last exercise and four additional ones (consisting of both natural and artificial images) to evaluate the accuracy and performance of the chosen parameters. Instead of using the supplied mask, however, we generate one randomly for every evaluation in order to prevent overfitting to a particular mask.

\subsubsection{Found values}
Our observations during the optimization process can be split into three classes:
\begin{itemize}
\item Some parameters converged towards their estimated value. The size of the Gaussian kernel, for example, has to be slightly bigger than the largest hole assumed in an image.
\item Some parameters have a clear speed vs. accuracy tradeoff, like the stopping conditions of the threshold optimization, which depend on our cost function and could not be foreseen.
\item Some parameters assumed totally different values than anticipated: The patch size became much larger and the validation set decreased significantly.
\end{itemize}

\section{Results}
We compared our algorithm with the following three baseline algorithms (see figure \ref{baseline_algorithms}):
\begin{enumerate}
\item Vertical and horizontal linear interpolation,
\item Gaussian interpolation as described in section \ref{gaussian_interpolation} and
\item Matching pursuit~\cite{matchingpursuit93} with an overcomplete dictionary of discrete cosines.
\end{enumerate}

@@

\paragraph{Note} All plots in this paper were created with MATLAB and can be reproduced using the script \emph{CreatePaperPlots.m} of our submission.

\section{Discussion}
Discuss the strengths and weaknesses of your approach, based on the results. Point out the implications of your novel idea on the application concerned.

>>>>

%\usepackage{times}
%\usepackage{balance}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage[pdftex]{hyperref}
\usepackage[utf8]{inputenc}

@@

\subsubsection{Gradient descent}
\label{gradient_descent}
We optimize all parameters at once using a gradient descent method. Since our cost function is based on measurements, we cannot derive it with respect to individual parameters and have to determine the gradient with finite differences. Besides weighting the parameters with respect to their improvements (which gives us the slope), we also defined a momentum term of 0.8 that should help us to overcome local minima and improve convergence speed. Figure \ref{gradient_descent_cost} shows the development of the cost for 100 optimisation steps.

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{../plots/cost_plot.pdf}
\caption{Due to the momentum term, the cost function does not strictly decrease when optimising.}
\label{gradient_descent_cost}
\end{figure}

@@

\begin{table*}
\centering
{\renewcommand{\arraystretch}{1.5}
\renewcommand{\tabcolsep}{0.2cm}
\begin{tabular}{|l|p{6cm}|p{6cm}|}
\hline
Function & Advantages & Disadvantages \\
\hline
$E + T$ & Easy to understand and everywhere a good gradient & Linear improvement does not necessarily follow one's intuition about the ordering of results \\
\hline
$\exp(E)+\exp(T)$ & Fast increase for both error and time & Not enough gradient for very low $E$ and $T$ values \\
\hline
$(1-\exp(E))*(1-\exp(T))$ & Allows very large times for very low errors & Also true vice versa, i.e. a minimization in time \\
\hline
$ \begin{cases}
E & \text{if }T<T_0\\
E+\exp(T/T_0 - 1) - 1 & \text{otherwise}
\end{cases} $ & Continuous function, optimizes for error when the time is below a target time $T_0$, penalizes long times. & Seems to work quite well, used by us \\
\hline
\end{tabular}}
\caption{Various cost functions used in the optimization process.}
\label{cost_functions}
\end{table*}

\subsubsection{Sample data}
We used the three images provided for the last exercise and four additional ones (consisting of both natural and artificial images, see figure \ref{new_images}) to evaluate the accuracy and performance of the chosen parameters. Instead of using the supplied mask, however, we generate one randomly for every evaluation in order to prevent overfitting to a particular mask.

\begin{figure*}
  \centering
  \subfloat{\includegraphics[width=0.22\textwidth]{../daisiesFromBing512x512}}~
  \subfloat{\includegraphics[width=0.22\textwidth]{../hardedges_512x512}}~
  \subfloat{\includegraphics[width=0.22\textwidth]{../penguinsFromBing512x512}}~
  \subfloat{\includegraphics[width=0.22\textwidth]{../velos512x512}}~
  \caption{The four additional images used during the optimisation.}
  \label{new_images}
\end{figure*}

\subsubsection{Found values}
Our observations during the optimization process can be split into three classes:
\begin{itemize}
\item Some parameters converged towards their estimated value. The size of the Gaussian kernel, for example, has to be slightly bigger than the largest hole assumed in an image.
\item Some parameters have a clear speed vs. accuracy tradeoff, like the stopping conditions of the threshold optimization, which depend on our cost function and could not be foreseen.
\item Some parameters assumed totally different values than anticipated: The patch size became much larger and the validation set decreased significantly, as can be seen in figure \ref{gradient_descent_parameters}.
\end{itemize}

\begin{figure}
  \centering
  \subfloat{\label{fig:gull}\includegraphics[width=0.25\textwidth]{../plots/td_middle_plot.pdf}}                
  \subfloat{\label{fig:tiger}\includegraphics[width=0.25\textwidth]{../plots/validation_plot.pdf}}
  \caption{Two parameters that seem to converge quite well during the optimisation.}
  \label{gradient_descent_parameters}
\end{figure}

\section{Results}
We compared our algorithm with the following three baseline algorithms (see figure \ref{baseline_algorithms}):
\begin{enumerate}
\item Vertical and horizontal linear interpolation,
\item Gaussian interpolation as described in section \ref{gaussian_interpolation} and
\item Matching pursuit~\cite{matchingpursuit93} with an overcomplete dictionary of discrete cosines. TODO this reference is wrong!
\end{enumerate}

@@

\paragraph{Note} All plots in this paper were created with MATLAB and were produced using the script \emph{CreatePaperPlots.m} of our submission. However, due to the randomness of the algorithm and varying speed measurements for the cost function, results can be different for each run.

\section{Discussion}
Discuss the strengths and weaknesses of your approach, based on the results. Point out the implications of your novel idea on the application concerned. TODO
